---
title: "Data 607 Assignment 9"
author: "Claire Meyer"
date: "4/7/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## NYT API

In this document, we'll be using the New York Times' Book Review API. Using their documentation, we're going to call to the API to grab the current hardcover nonfiction list.

```{r libraries, echo=FALSE}
library(tidyverse)
library(jsonlite)
```

```{r api-call}
url <- 'https://api.nytimes.com/svc/books/v3/lists/current/hardcover-nonfiction.json?api-key=3ImZ9GGsnMCDHHePNZ6IXzTpHT5qh98O'

raw_results <- fromJSON(txt = url)
books_df <- raw_results$results$books
```


## Analysis

Then, we can do some lightweight analysis to see how long some of these books have been on the list, and their makeup. 

We find that there is only one brand new entrant to the list ("REMEMBER"), with a couple outliers with more than 20 weeks on the list ("UNTAMED" and "HOW TO BE AN ANTIRACIST").

```{r book-analysis}
summary(books_df$weeks_on_list)
```

```{r boxplot}
boxplot(books_df$weeks_on_list)
```

```{r hist}
ggplot(books_df, aes(books_df$weeks_on_list)) + geom_histogram(binwidth = 1)
```